Automated discovery of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Clean SR methods

Symbolic regression is a machine learning (ML) algorithm for regression which searches the space of analytic expressions that fit some dataset.
Whereas most ML algorithms are optimized by fitting a fixed set number of real parameters, symbolic regression is typically done using a ``genetic algorithm'' which finds a tree or sequence of symbols that optimizes an objective.
Since models for physical phenomena are often specified in a language of concise mathematical expressions, symbolic regression can produce very interpretable models compared to traditional ML, as the ``trained model'' generated by symbolic regression is in the same language as existing physical models.
Therefore, symbolic regression can produce insights for science in a way that traditional ML cannot.

>>>>

Symbolic regression is a machine learning (ML) algorithm for regression which searches  for analytic expressions which optimize some loss function.
Whereas one can fit most ML algorithms to data by optimizing a fixed set number of real parameters, for symbolic regression, one typically uses using a ``genetic algorithm.'' This genetic algorithm arranges symbols in a tree, evaluates the resultant expression, and repeats this process until a particular goal is met.
Since models for physical phenomena are often specified in a language of concise mathematical expressions, symbolic regression can produce very interpretable models compared to traditional ML, as the ``trained model'' generated by symbolic regression is in the same \textit{language} as existing physical models (i.e., analytic expressions).
Therefore, symbolic regression can produce insights for science in a way that traditional ML cannot.
